---
title: "Data Exploratory Analyses/Plots"
author: "Kathryn Wheeler"
date: "11/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
source('sharedVariables.R')
source('NEON_Data_DownloadAndProcess.R')
library(MuMIn)
library(ggplot2)
library(mgcv)
library(ggridges)
```

#Load Covariate Data
```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE}
allPrecipData <- read.csv(paste0(dataPath,"NEON_PrecipitationDataDailydata_gapFilled.csv"))
allPrecipData$year <- lubridate::year(allPrecipData$date)
allPrecipData <- allPrecipData %>% group_by(year,siteID) %>% mutate(cumPrecip=cumsum(precipBulk)) #Calculates the cummulative sum of precip for each site-year for each date

allTempData <- read.csv(paste0(dataPath,"NEON_TemperatureDataDailydata_gapFilled.csv"))
allTempData$year <- lubridate::year(allTempData$date)

allTempData$GDDoffset_0 <- ifelse((allTempData$tempTripleMean-0)<0,0,allTempData$tempTripleMean-0)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_0=cumsum(GDDoffset_0))

allTempData$GDDoffset_5 <- ifelse((allTempData$tempTripleMean-5)<0,0,allTempData$tempTripleMean-5)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_5=cumsum(GDDoffset_5))

allTempData$GDDoffset_10 <- ifelse((allTempData$tempTripleMean-10)<0,0,allTempData$tempTripleMean-10)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_10=cumsum(GDDoffset_10))

allTempData$GDDoffset_15 <- ifelse((allTempData$tempTripleMean-15)<0,0,allTempData$tempTripleMean-15)
allTempData <- allTempData %>% group_by(year,siteID) %>% mutate(GDD_15=cumsum(GDDoffset_15))

allTempData <- allTempData[,-c(5,7,9,11)] #Remove the offset columns to just keep cummulative 

allSunlightTimes <- read.csv(paste0(dataPath,'NEON_sunlightTimes.csv'))[-c(3,4,5,6)]
```

#For each site-PFT combination: How many individuals of the different associations are present? 

```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=15}
#Number of Individuals of AM and EcM that are present
uniqueIndividuals <- matrix(nrow=0,ncol=5)
for(p in seq_along(NEON_phenophase_names)){
  #Bud burst 
  print(NEON_phenophase_names[p])

  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat[,c('siteID','individualID','growthForm','Mycorrhizal.type','decimalLatitude')]
  subDat <- subDat %>% unique()
  uniqueIndividuals <- rbind(uniqueIndividuals,subDat)
  uniqueIndividuals <- uniqueIndividuals %>% unique()
}
uniqueIndividuals <- uniqueIndividuals[!(uniqueIndividuals$siteID%in%c("2019","2020","2021","2017","2018","2022")),]
#uniqueIndividuals <- uniqueIndividuals %>% filter(Mycorrhizal.type %in% c("AM","EcM"))
uniqueIndividuals <- uniqueIndividuals %>% filter(!is.na(growthForm))
uniqueIndividuals[uniqueIndividuals$growthForm=="Pine",'growthForm'] <- "Evergreen conifer"
uniqueIndividuals <- uniqueIndividuals %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) #Exclude the others 

uniqueIndividuals2 <- uniqueIndividuals %>% group_by(siteID,Mycorrhizal.type,growthForm,decimalLatitude) %>% summarise(n=n())

ggplot(uniqueIndividuals2,aes(fill=Mycorrhizal.type,y=n,x=fct_reorder(siteID,decimalLatitude))) + 
  geom_bar(position="dodge",stat="identity")+
  facet_wrap(~growthForm,ncol=4)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Site ID (Ordered by Latitude)")+
  ylab("Number of Individuals")+
  coord_flip()

```


What I learned is that DB has the best variation between different mycorrhizal associations so that's where I should focus my comparitive studies and then do across PFTs for the overall. 

#For each phenophase, what growth forms (PFT) are measured?
```{r,echo=FALSE,message=FALSE,warning=FALSE}
allDat <- matrix(nrow=0,ncol=6)
for(p in seq_along(NEON_phenophase_names)){
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat[,c('siteID','individualID','growthForm','decimalLatitude','year','phenophaseName')]
  subDat <- subDat %>% unique() %>% filter(!is.na(growthForm))
  allDat <- rbind(allDat,subDat)
}
  allDat <- allDat %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf"))
  
  growthFormTotal <- allDat %>% group_by(growthForm) %>% summarise(growthFormTotal=n())
  allDat <- left_join(allDat,growthFormTotal,by="growthForm")
    
  allDat2 <- allDat %>% group_by(phenophaseName,growthForm,growthFormTotal) %>% summarise(n=(n()))
  # ggplot(allDat2,aes(n,phenophaseName,fill=growthForm)) +
  #           geom_bar(position="dodge",stat="identity")+
  #           scale_fill_brewer(palette="Accent")+
  #           theme_classic()+
  #           theme(axis.text.x = element_text(angle=90))+
  #           xlab("Number Of Total Measurements (Ratio of Total Per Growth Form")+
  #           ylab("Phenophase")+
  #           ggtitle(NEON_phenophase_names[p])
  
    ggplot(allDat2,aes((n/growthFormTotal),growthForm,fill=phenophaseName)) +
            geom_bar(position="dodge",stat="identity")+
            scale_fill_brewer(palette="Set3")+
            theme_classic()+
            theme(axis.text.x = element_text(angle=90))+
            xlab("Number Of Total Measurements (Ratio of Total Per Growth Form)")+
            ylab("Growth Form")+
            ggtitle("Which Phenophases are Monitored for with Growth Forms")

```

What I learned: Measured phenophases differ a lot by PFT. Evergreen don't have an end of growing season measurement. Many just have leaves as their changing phenophase. 

#For each site-phenophase combination: how many years are individuals re-measured by mycorrhizae type?
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.width=8,fig.height=10}
for(p in seq_along(NEON_phenophase_names)){
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','year')]
  subDat <- subDat %>% unique()
  
  subDat2 <- subDat %>% group_by(siteID,Mycorrhizal.type,individualID,decimalLatitude) %>% summarise(n=n())
  if(nrow(subDat2)>2){
    print(ggplot(subDat2,aes(n,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
            geom_density_ridges2(scale=1)+
            theme_classic()+
            theme(axis.text.x = element_text(angle=90))+
            xlab("Number Of Years Per Individual")+
            ylab("Site ID (Ordered by Latitude)")+
            ggtitle(NEON_phenophase_names[p])+
            scale_x_continuous(limits=c(0,8)))
  }
}

```

What I learned: There aren't large sample sizes per individual and the sample sizes range between 1 and 8. 

#For each PFT-phenophase combination: Does the timing in DOYs differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?

```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
for(p in seq_along(NEON_phenophase_names)){
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  subDat <- subDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm')]
  subDat <- subDat %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Forb","Graminoid"))
  
  if(nrow(subDat)>2){
    print(ggplot(subDat,aes(dayOfYear,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
            geom_density_ridges2(scale=1)+
            theme_bw()+
            theme(axis.text.x = element_text(angle=90))+
            xlab("DOY")+
            ylab("Site ID (Ordered by Latitude)")+
            facet_wrap(~growthForm)+
            ggtitle(NEON_phenophase_names[p]))
          #+
           # scale_x_continuous(limits=c(0,100)))
  }
}
  
```

What I learned: For most sites, AM budburst earlier and senescened earlier than ECM

#For each PFT-phenophase combination: Does the Standard Deviation in DOYs differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?

```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
for(p in seq_along(NEON_phenophase_names)){
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  subDat <- subDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm')]
  subDat <- subDat %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Forb","Graminoid"))
  subDat2 <- subDat %>% group_by(individualID) %>% mutate(doy_sd=sd(dayOfYear,na.rm=TRUE))
  
  if(nrow(subDat2)>2){
    print(ggplot(subDat2,aes(doy_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
            geom_density_ridges2(scale=1)+
            theme_bw()+
            theme(axis.text.x = element_text(angle=90))+
            xlab("SD in DOY Per Individual")+
            ylab("Site ID (Ordered by Latitude)")+
            facet_wrap(~growthForm)+
            ggtitle(NEON_phenophase_names[p])+
            scale_x_continuous(limits=c(0,100)))
  }
}
  
```

What I learned: EcM seem maybe have less sd in timing in budburst. SD in Colored leaves doesn't seem to differ as much between mycorrhizae types. 

New question: Do they break buds earlier when corrected for site or latitude effects? 

#For each PFT-phenophase combination: Does the length of winter and summer differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?

##There are various definitions of growing season length depending on PFT:
*Semi-evergreen broadleaf: budburst-colored; leaves (varying intensities); Young-leaves-colored
*Graminoid: leaves (varying intensities)
*Forb: leaves (varying intensities); Young-leaves-colored
*Evergreen conifer: No lengths
*Evergreen broadleaf: No lengths
*Drought deciduous broadleaf: leaves (varying intensities); young leaves-colored leaves
*Deciduous broadleaf: leaves (varying intensities); budburst-colored 

##Different definitions of growing season length:
*Budburst-colored: semi-evergreen broadleaf; deciduous broadleaf
*Leaf presence: semi-evergreen broadleaf; graminoid; forb; drought deciduous broadleaf; deciduous broadleaf
*Young-leaves-colored:semi-evergreen broadleaf; forb; drought-deciduous broadleaf

```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
for(initialP in c(1,2)){
  p=initialP
  budBurstDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  budBurstDat <- budBurstDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  
  budBurstDat <- budBurstDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')] %>% mutate(winterYear=as.numeric(year),year=as.numeric(year))
  
  p=3
  coloredLeavesDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  coloredLeavesDat <- coloredLeavesDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  
  coloredLeavesDat <- coloredLeavesDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')]%>% mutate(winterYear=(year+1),year=as.numeric(year))
  
  winterLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
                            by=c("winterYear","individualID",'siteID',"Mycorrhizal.type","decimalLatitude",
                                     "growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf"))%>% 
    mutate(winterLength=as.Date(date.y)-as.Date(date.x))
  
  summerLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
                                by=c("year","individualID",'siteID',"Mycorrhizal.type",
                                     "decimalLatitude","growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) %>%
    mutate(summerLength=as.Date(date.x)-as.Date(date.y))
  
  print(ggplot(winterLengthDat,
         aes(winterLength,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
    geom_density_ridges2(scale=1)+
    theme_bw()+
    theme(axis.text.x = element_text(angle=90))+
    xlab("Winter Length (days)")+
    ylab("Site ID (Ordered by Latitude)")+
    facet_wrap(~growthForm)+
    ggtitle(paste("Winter Length Per Individual: Colored-",NEON_phenophase_names[initialP])))
  
    print(ggplot(summerLengthDat,
         aes(summerLength,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
    geom_density_ridges2(scale=1)+
    theme_bw()+
    theme(axis.text.x = element_text(angle=90))+
    xlab("Summer Length (days)")+
    ylab("Site ID (Ordered by Latitude)")+
    facet_wrap(~growthForm)+
    ggtitle(paste("Summer Length Per Individual: Colored-",NEON_phenophase_names[initialP])))
  
}
# #Based on Leaf Numbers
# leavesPhenophases <- determinePhenophaseTimingForLeaves(dataPath) %>% 
#   filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) 
# 
# greenupDat <- leavesPhenophases %>% dplyr::select(-c(greendownDate,greendownDOY)) %>%
#   mutate(winterYear=(year),year=as.numeric(year))
# greendownDat <- leavesPhenophases %>% dplyr::select(-c(greenupDate,greenupDOY)) %>%
#   mutate(winterYear=(year+1),year=as.numeric(year))
# 
# winterLengthDat <- inner_join(greendownDat,greenupDat,
#                                 by=c("winterYear","individualID",'siteID',"Mycorrhizal.type",
#                                      "decimalLatitude","growthForm")) %>%
#   mutate(winterLength=as.Date(greenupDate)-as.Date(greendownDate)) %>%
#     group_by(individualID) %>% mutate(winter_sd=sd(winterLength,na.rm=TRUE)) %>%
#     ungroup() %>%
#     dplyr::select(individualID,winter_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
#   
#   summerLengthDat <- inner_join(greendownDat,greenupDat,
#                                 by=c("year","individualID",'siteID',"Mycorrhizal.type",
#                                      "decimalLatitude","growthForm")) %>%
#   mutate(summerLength=as.Date(greendownDate)-as.Date(greenupDate)) %>%
#     group_by(individualID) %>% mutate(summer_sd=sd(summerLength,na.rm=TRUE)) %>%
#     ungroup() %>%
#     dplyr::select(individualID,summer_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
#   
#   ggplot(winterLengthDat,
#          aes(winter_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
#     geom_density_ridges2(scale=1)+
#     theme_bw()+
#     theme(axis.text.x = element_text(angle=90))+
#     xlab("SD")+
#     ylab("Site ID (Ordered by Latitude)")+
#     facet_wrap(~growthForm)+
#     ggtitle(paste("SD in Winter Length Per Individual: Number of Leaves"))+
#     scale_x_continuous(limits=c(0,50))
#   
#     ggplot(summerLengthDat,
#          aes(summer_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
#     geom_density_ridges2(scale=1)+
#     theme_bw()+
#     theme(axis.text.x = element_text(angle=90))+
#     xlab("SD")+
#     ylab("Site ID (Ordered by Latitude)")+
#     facet_wrap(~growthForm)+
#     ggtitle(paste("SD in Summer Length Per Individual: Number of Leaves"))+
#     scale_x_continuous(limits=c(0,50))
#   

```

What I learned: EcM maybe has a slightly shorter winter and AM maybe has a slightly shorter summer. 

#For each PFT-phenophase combination: Does the SD of winter and summer lengths differ between phenophases differ between EcM and AM associated plants acrross all sites and within each site?

```{r,echo=FALSE,results='hide',message=FALSE,warning=FALSE,fig.width=10,fig.height=20}
for(initialP in c(1,2)){
  p=initialP
  budBurstDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  budBurstDat <- budBurstDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  
  budBurstDat <- budBurstDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')] %>% mutate(winterYear=as.numeric(year),year=as.numeric(year))
  
  p=3
  coloredLeavesDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  coloredLeavesDat <- coloredLeavesDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  
  coloredLeavesDat <- coloredLeavesDat[,c('siteID','individualID','Mycorrhizal.type','decimalLatitude','dayOfYear','growthForm','year','date')]%>% mutate(winterYear=(year+1),year=as.numeric(year))
  
  winterLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
                            by=c("winterYear","individualID",'siteID',"Mycorrhizal.type","decimalLatitude",
                                     "growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf"))%>% 
    mutate(winterLength=as.Date(date.y)-as.Date(date.x)) %>%
    group_by(individualID) %>% mutate(winter_sd=sd(winterLength,na.rm=TRUE)) %>%
    ungroup() %>%
    dplyr::select(individualID,winter_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
  
  summerLengthDat <- inner_join(coloredLeavesDat,budBurstDat,
                                by=c("year","individualID",'siteID',"Mycorrhizal.type",
                                     "decimalLatitude","growthForm")) %>% filter(growthForm %in% c("Deciduous broadleaf","Drought deciduous broadleaf","Evergreen broadleaf","Evergreen conifer","Forb","Graminoid","Semi-evergreen broadleaf")) %>%
    mutate(summerLength=as.Date(date.x)-as.Date(date.y)) %>%
    group_by(individualID) %>% mutate(summer_sd=sd(summerLength,na.rm=TRUE))%>%
    ungroup() %>%
    dplyr::select(individualID,summer_sd,siteID,Mycorrhizal.type,decimalLatitude,growthForm) %>% unique()
  
  print(ggplot(winterLengthDat,
         aes(winter_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
    geom_density_ridges2(scale=1)+
    theme_bw()+
    theme(axis.text.x = element_text(angle=90))+
    xlab("SD")+
    ylab("Site ID (Ordered by Latitude)")+
    facet_wrap(~growthForm)+
    ggtitle(paste("SD in Winter Length Per Individual: Colored-",NEON_phenophase_names[initialP]))+
    scale_x_continuous(limits=c(0,100)))
  
    print(ggplot(summerLengthDat,
         aes(summer_sd,fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
    geom_density_ridges2(scale=1)+
    theme_bw()+
    theme(axis.text.x = element_text(angle=90))+
    xlab("SD")+
    ylab("Site ID (Ordered by Latitude)")+
    facet_wrap(~growthForm)+
    ggtitle(paste("SD in Summer Length Per Individual: Colored-",NEON_phenophase_names[initialP]))+
    scale_x_continuous(limits=c(0,100)))
}

```

What I learned: The standard deviations in winter and summer lengths don't really seem to differ between EcM and AM. 

#For each individual and phenophase, what predictors seem to be the most important?

```{r}
p=5

```


#For each site, do the covariates that occur with each phenophase differ between MTs? 
```{r}
p <- 2 #Bud burst 
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p],
                              growthForm=="Deciduous broadleaf")
  subDat$year <- as.numeric(subDat$year)
  subDat <- left_join(subDat,allPrecipData[,-3],by=c('siteID','date','year'))
  subDat <- left_join(subDat,allTempData,by=c('siteID','date','year'))
  subDat <- left_join(subDat,allSunlightTimes,by=c('siteID','date'))
  
  ggplot(subDat,aes(as.numeric(as.character(GDD_10)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_10 (C)")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("GDD_10 of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,600))
  
    ggplot(subDat,aes(as.numeric(as.character(GDD_5)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_5 (C)")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("GDD_5 of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,600))
    
  ggplot(subDat,aes(as.numeric(as.character(daylength)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Daylength (hours)")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Daylength of Bud Burst in Deciduous Broadleaf")
  
    ggplot(subDat,aes(as.numeric(as.character(height)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Plant Height")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Plant Height in Deciduous Broadleaf")
  
```

What I learned: I don't really see patterns in if a MT covariates varied more for one that the other. 

AM-associated plants are shorter than the EcM-associated ones so the earlier budburst is really just like because they are understory plants. Well crap. 

#Do the basic GAMs work for any of the phenophase and PFTs?

```{r}
p <- 2 #Bud burst 
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p],
                              growthForm=="Deciduous broadleaf")
  subDat$year <- as.numeric(subDat$year)
  
  allIndividuals <- unique(subDat$individualID)
  subDat <- subDat %>% dplyr::select(siteID,date,dayOfYear,individualID,canopyPosition,
                           height,growthForm,Mycorrhizal.type,year)

  allOutput <- matrix(nrow=0,ncol=10)
  colnames(allOutput) <- c('siteID','date','dayOfYear','individualID',
                           'canopyPosition','height','growthForm',
                           'Mycorrhizal.type','year','phenophaseOccurred')
  for(i in seq_along(allIndividuals)){
    if(i %% 100==0){
      print(i)
    }
    subSubDat <- subDat %>% filter(individualID==allIndividuals[i])
    for(j in 1:nrow(subSubDat)){
      currentRow <- subSubDat[j,]
      newOutput <- currentRow %>% slice(rep(1:n(), each = (subSubDat$dayOfYear[j]-1)))
      newOutput <- as.data.frame(newOutput)
      newOutput$date <- seq((as.Date(currentRow$date)-currentRow$dayOfYear+1),
                            (as.Date(currentRow$date)-1),by="day")
      newOutput$dayOfYear <- as.integer(row.names(newOutput))
      newOutput$phenophaseOccurred <- FALSE
      currentRow$phenophaseOccurred <- TRUE
      newOutput <- rbind(newOutput,currentRow)
      newOutput <- newOutput[(max((nrow(newOutput)-29),0)):nrow(newOutput),]

      allOutput <- rbind(allOutput,newOutput)
    }
    
  }
  OGallOutput <- allOutput
  allOutput$date <- as.character(as.Date(allOutput$date))
  allOutput <- left_join(allOutput,allPrecipData[,-3],by=c('siteID','date','year'))
  allOutput <- left_join(allOutput,allTempData,by=c('siteID','date','year'))
  allOutput <- left_join(allOutput,allSunlightTimes,by=c('siteID','date'))
  allOutput <- allOutput %>% filter(year!=2022)
  allOutput$Mycorrhizal.type <- as.factor(allOutput$Mycorrhizal.type)
  
  #Deciduous Broadleaf
  subDatDB <- allOutput %>% filter(growthForm=="Deciduous broadleaf",canopyPosition %in% c("Mostly shaded","Partially shaded","Full sun","Full shade"))
  
  # mdl_gam1 <- gam(dayOfYear ~ s(GDD_15,k=10) + s(GDD_5,k=10) + s(GDD_0,k=10) + s(GDD_10,k=10),data=subDatDB,
  #                  method="REML",
  #                  na.action="na.fail")
  
  mdl_gam <- gam(phenophaseOccurred ~ s(GDD_10) + s(daylength),data=subDatDB,
                   method="REML",
                   na.action="na.fail")
  
  mdl <- lm <- lm(phenophaseOccurred ~ (GDD_10) + (daylength),data=subDatDB)
  #######********Editing here: How to get it to predict a categorical response variable?****
  
  gam.check(mdl_gam,page=1)
  plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
  gam.check(mdl_gam1,page=1)
  
  plot(subDatDB$daylength,subDatDB$dayOfYear,pch=20)
  plot(subDatDB$GDD_5,subDatDB$dayOfYear,pch=20)
  plot(subDatDB$cumPrecip,subDatDB$dayOfYear,pch=20)
  
  mdl_gam2 <- gam(dayOfYear ~ s(daylength,by=Mycorrhizal.type) + s(GDD_10,by=Mycorrhizal.type) + s(cumPrecip,by=Mycorrhizal.type) + ,data=subDatDB,
                   method="REML",
                   na.action="na.fail")
  
    plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
      gam.check(mdl_gam1,page=1)
  
  
```

#Is phenology correlated with soil microbial biodiversity? 
```{r}
allBioDat <- read.csv(paste0(dataPath,dataName,"/soilMicrobediversityData.csv"))

allPlotIDLatLong <- matrix(nrow=0,ncol=3)
for(s in seq_along(NEON_siteNames)){
  print(NEON_siteNames[s])
  files <- dir(path=paste0(dataPath,'NEON_presence-cover-plant-CLEAN'),
               pattern=NEON_siteNames[s])
  for(f in 1:5){
    subDat <- read.csv(paste0(dataPath,'NEON_presence-cover-plant-CLEAN/',files[f]))[,c('decimalLatitude','decimalLongitude','plotID')] %>% unique()
    allPlotIDLatLong <- rbind(allPlotIDLatLong,subDat)
  }
}

allPlotIDLatLong <- allPlotIDLatLong %>% unique()
allBioDat <- left_join(allBioDat,allPlotIDLatLong,by="plotID")

phenoCamURLs <- read.csv(paste0(dataPath,'phenocamURLS.csv'))

files <- dir(path=paste0(dataPath,'phenoCamData'),pattern="dates")
allPCdat <- matrix(nrow=0,ncol=19)
for(f in seq_along(files)){
  subDat <- read.csv(paste0(dataPath,'phenoCamData/',files[f]),skip=16) %>%
    filter(gcc_value=="gcc_90")
  allPCdat <- rbind(allPCdat,subDat)
  
}
allPCdat_cleaned <- matrix(nrow=0,ncol=8)
subDat <- allPCdat[,c('site','veg_type','roi_id','direction',
                                                   'transition_15','transition_15_lower_ci',
                                                   'transition_15_upper_ci')]
colnames(subDat) <- c('site','veg_type','roi_id','direction',
                                                   'date','lower_ci',
                                                   'upper_ci')
subDat$transition <- 15
allPCdat_cleaned <- rbind(allPCdat_cleaned,subDat)
subDat <- allPCdat[,c('site','veg_type','roi_id','direction',
                                                   'transition_50','transition_50_lower_ci',
                                                   'transition_50_upper_ci')]
colnames(subDat) <- c('site','veg_type','roi_id','direction',
                                                   'date','lower_ci',
                                                   'upper_ci')
subDat$transition <- 50
allPCdat_cleaned <- rbind(allPCdat_cleaned,subDat)
subDat <- allPCdat[,c('site','veg_type','roi_id','direction',
                                                   'transition_85','transition_85_lower_ci',
                                                   'transition_85_upper_ci')]
colnames(subDat) <- c('site','veg_type','roi_id','direction',
                                                   'date','lower_ci',
                                                   'upper_ci')
subDat$transition <- 85
allPCdat_cleaned <- rbind(allPCdat_cleaned,subDat)
allPCdat_cleaned$siteID <- sapply(strsplit(as.character(allPCdat_cleaned$site), "[.]"), `[`, 3)
allPCdat_cleaned <- left_join(allPCdat_cleaned,allTempData,by=c('siteID','date'))
allPCdat_cleaned <- left_join(allPCdat_cleaned,allSunlightTimes,by=c('siteID','date'))
allPCdat_cleaned <- left_join(allPCdat_cleaned,allPrecipData,by=c('siteID','date','year'))

phenoCam_siteData <- read.csv(paste0(dataPath,"NEON_PhenoCam_SiteData.csv"))
phenoCam_siteData$siteID <- sapply(strsplit(as.character(phenoCam_siteData$phenoCamID), "[.]"), `[`, 3)

allPlotIDLatLong$difference <- NA
allPlotIDLatLong$siteID <- sapply(strsplit(as.character(allPlotIDLatLong$plotID), "_"), `[`, 1)
allPlotIDLatLong <- left_join(allPlotIDLatLong,phenoCam_siteData,by="siteID")
allPlotIDLatLong$direction[is.na(allPlotIDLatLong$direction)] <- "N" #Assume missing directions are North because most cameras are pointed North
allPlotIDLatLong[allPlotIDLatLong$direction=="N",'difference'] <- allPlotIDLatLong[allPlotIDLatLong$direction=="N",'decimalLatitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="N",'Lat']

allPlotIDLatLong[allPlotIDLatLong$direction=="W",'difference'] <- allPlotIDLatLong[allPlotIDLatLong$direction=="W",'decimalLongitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="W",'Lon']

allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'difference'] <- sqrt((allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'decimalLongitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'Lon'])**2 + (allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'decimalLatitude']-allPlotIDLatLong[allPlotIDLatLong$direction=="NNE",'Lat'])**2)

allPlotIDLatLong_filtered <- allPlotIDLatLong[allPlotIDLatLong$difference>0,] %>%
  filter(direction!="NNE") #Deal with NNE later because it's more complicated because latitude and longitude differences have to be positive 

allPlotIDLatLong_filtered <- allPlotIDLatLong_filtered %>% group_by(siteID) %>%
  slice(which.min(difference))

allBioDat_plotFiltered <- allBioDat %>% 
  filter(plotID %in% allPlotIDLatLong_filtered$plotID) %>%
  mutate(year=lubridate::year(date))%>%
  group_by(year,siteID) %>%
  summarise(year_totalSpecies=sum(totalSpecies),year_totalIndividual=sum(totalIndividuals))


allBioDat_plotFiltered$biodiversity <- allBioDat_plotFiltered$year_totalSpecies/allBioDat_plotFiltered$year_totalIndividual


allPCdat_cleaned_15 <- allPCdat_cleaned %>% filter(direction=="rising",transition==15,veg_type=="DB")

allBioDat_plotFiltered_15 <- left_join(allBioDat_plotFiltered,allPCdat_cleaned_15,by=c('year','siteID'))

plot(allBioDat_plotFiltered_15$biodiversity,allBioDat_plotFiltered_15$GDD_0,pch=20)
mdl <- lm(GDD_0~biodiversity,data = allBioDat_plotFiltered_15)
abline(mdl)
summary(mdl)

```

What I learned: There might be some positive correlations between soil microbe biodiversity and phenocam, but there aren't enough site-years to test because soil microbe data started years before phenocam, but is 4 years delayed.

#Extra Code
```{r,eval=FALSE}
p <- 2 #Bud burst 
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  subDat$year <- as.numeric(subDat$year)
  subDat <- left_join(subDat,allPrecipData[,-3],by=c('siteID','date','year'))
  subDat <- left_join(subDat,allTempData,by=c('siteID','date','year'))
  subDat <- left_join(subDat,allSunlightTimes,by=c('siteID','date'))
  subDat <- subDat %>% filter(year!=2022)
  subDat$Mycorrhizal.type <- as.factor(subDat$Mycorrhizal.type)
  
  #Deciduous Broadleaf
  subDatDB <- subDat %>% filter(growthForm=="Deciduous broadleaf")
  subDatDB_ECM <- subDatDB %>% filter(Mycorrhizal.type=="EcM",growthForm=="Deciduous broadleaf")
  subDatDB_AM <- subDatDB %>% filter(Mycorrhizal.type=="AM",growthForm=="Deciduous broadleaf")
  
  plot(density(subDatDB_AM$dayOfYear),main="Day of Year of Budburst for DB")
  lines(density(subDatDB_ECM$dayOfYear),col="red")
  legend('topleft',col=c("black","red"),legend = c("AM DB","ECM DB"),lty=1)
  
  ggplot(subDatDB,aes(as.numeric(as.character(dayOfYear)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Day of Year of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,200))
  
    ggplot(subDatDB,aes(as.numeric(as.character(dayOfYear)),Genus,fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Day of Year of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,200))
    
    output <- matrix(ncol=length(unique(subDatDB$Genus)),nrow=length_NEON_siteNames)
    for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      for(j in seq_along(unique(subDatDB$Genus))){
        output[s,j] <- nrow(subDatDB %>% 
                              filter(Genus==(unique(subDatDB$Genus)[j]),siteID==NEON_siteNames[s]))
      }
    }
    speciesPerSite <- data.frame(output)
    colnames(speciesPerSite) <- unique(subDatDB$Genus)
    speciesPerSite <- cbind(NEON_siteNames,speciesPerSite)
    
    MTperSite <- data.frame(matrix(ncol=6,nrow=length_NEON_siteNames))
    colnames(MTperSite) <- c("siteID","Total_AM_ind","Total_ECM_ind","Total_AM_gen","Total_ECM_gen","Lat")
    MTperSite$siteID <- NEON_siteNames
    for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      siteDat <- subDatDB %>% filter(siteID==NEON_siteNames[s])
      MTperSite$Total_AM_ind[s] <- sum(siteDat$Mycorrhizal.type=="AM")
      MTperSite$Total_ECM_ind[s] <- sum(siteDat$Mycorrhizal.type=="EcM")
      MTperSite$Total_AM_gen[s] <- length(unique((siteDat %>% filter(Mycorrhizal.type=="AM"))$Genus))
      MTperSite$Total_ECM_gen[s] <- length(unique((siteDat %>% filter(Mycorrhizal.type=="EcM"))$Genus))
      MTperSite$Lat[s] <- as.numeric(siteData[siteData$field_site_id==NEON_siteNames[s],'field_latitude'])
    }
    MTperSite <- MTperSite[order(MTperSite$Lat,decreasing = TRUE),]
    
    mdl_gam <- gam(dayOfYear ~ s(decimalLatitude,k=25) + Mycorrhizal.type,data=subDatDB,
                   method="REML",
                   na.action="na.fail")
    plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
      gam.check(mdl_gam,page=1)
    plot(subDatDB$decimalLatitude,subDatDB$dayOfYear,pch=20,xlab="Latitude",ylab="Day Of Year of Budburst")
    abline(lm(dayOfYear ~ decimalLatitude,data=subDatDB),lwd=3)
    abline(lm(dayOfYear ~ decimalLatitude,data=subDatDB[subDatDB$Mycorrhizal.type=="AM",]),lwd=3,col="cyan")
    abline(lm(dayOfYear ~ decimalLatitude,data=subDatDB[subDatDB$Mycorrhizal.type=="EcM",]),lwd=3,col="red")
    legend('bottomright',col=c("black","cyan","red"),legend = c("All DB","AM DB","ECM DB"),lty=1,lwd=3)
    
  concurvity(mdl_gam,full=TRUE)
  
  ggplot(subDatDB,aes(as.numeric(as.character(GDD_10)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_10 (C)")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("GDD_10 of Bud Burst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,600))
      
      ggplot(subDatDB,aes(as.numeric(as.character(GDD_10)),as.numeric(as.character(dayOfYear)),col=Mycorrhizal.type))+geom_point(cex=.1)+
        facet_wrap(~siteID,ncol=6)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_10 (C)")+
  ylab("Day of Year of Budburst")+
        geom_smooth(method="lm")+ 
  scale_x_continuous(limits=c(0,1500))
      
  gdd_doy_slopes <- data.frame(matrix(nrow=length_NEON_siteNames,ncol=3))
  colnames(gdd_doy_slopes) <- c("siteID","AM_slope","ECM_slope")
  gdd_doy_slopes$siteID <- NEON_siteNames
  for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      siteDat <- subDatDB %>% filter(siteID==NEON_siteNames[s])
      if(sum(siteDat$Mycorrhizal.type=="AM")>1){
      gdd_doy_slopes$AM_slope[s] <- summary(lm(dayOfYear~GDD_10,
                                               data=siteDat[siteDat$Mycorrhizal.type=="AM",]))$coefficients[2,1]
      }
      if(sum(siteDat$Mycorrhizal.type=="EcM")>3){
      gdd_doy_slopes$ECM_slope[s] <- summary(lm(dayOfYear~GDD_10,
                                               data=siteDat[siteDat$Mycorrhizal.type=="EcM",]))$coefficients[2,1]
      }
  }
  plot(density(na.omit(gdd_doy_slopes$AM_slope)),col="cyan",main="Slopes of Site-Specific Linear Regressions Between GDD_10 and DOY of Bud Burst")
  lines(density(na.omit(gdd_doy_slopes$ECM_slope)),col="red")
  legend('topright',col=c("cyan","red"),legend = c("AM DB","ECM DB"),lty=1,lwd=3)
  
  dl_doy_slopes <- data.frame(matrix(nrow=length_NEON_siteNames,ncol=3))
  colnames(dl_doy_slopes) <- c("siteID","AM_slope","ECM_slope")
  dl_doy_slopes$siteID <- NEON_siteNames
  for(s in seq_along(NEON_siteNames)){
      print(NEON_siteNames[s])
      siteDat <- subDatDB %>% filter(siteID==NEON_siteNames[s])
      if(sum(siteDat$Mycorrhizal.type=="AM")>1){
      dl_doy_slopes$AM_slope[s] <- summary(lm(dayOfYear~daylength,
                                               data=siteDat[siteDat$Mycorrhizal.type=="AM",]))$coefficients[2,1]
      }
      if(sum(siteDat$Mycorrhizal.type=="EcM")>3){
      dl_doy_slopes$ECM_slope[s] <- summary(lm(dayOfYear~daylength,
                                               data=siteDat[siteDat$Mycorrhizal.type=="EcM",]))$coefficients[2,1]
      }
  }
  plot(density(na.omit(dl_doy_slopes$AM_slope)),col="cyan",main="Slopes of Site-Specific Linear Regressions Between Day length and DOY of Bud Burst")
  lines(density(na.omit(dl_doy_slopes$ECM_slope)),col="red")
  legend('topright',col=c("cyan","red"),legend = c("AM DB","ECM DB"),lty=1,lwd=3)
  
  mdl_gam <- gam(dayOfYear ~ s(daylength, by=as.factor(siteID)) + Mycorrhizal.type,data=subDatDB,
                 method="REML",
                 na.action="na.fail")
    plot.gam(mdl_gam,residuals=TRUE,pch=20,cex=5,shade=TRUE,page=1,all.terms = TRUE)
    gam.check(mdl_gam)
    
    plot(subDatDB$daylength,subDatDB$dayOfYear,pch=20)
    points(subDatDB[subDatDB$Mycorrhizal.type=="EcM",'daylength'],
           subDatDB[subDatDB$Mycorrhizal.type=="EcM",'dayOfYear'],pch=20,col="red")
    
    points(subDatDB[subDatDB$Mycorrhizal.type=="AM",'daylength'],
           subDatDB[subDatDB$Mycorrhizal.type=="AM",'dayOfYear'],pch=20,col="cyan")
    

    
    subDatDB2 <- subDatDB %>% group_by(individualID) %>% mutate(doy_sd=sd(dayOfYear,na.rm=TRUE))
    subDatDB2 <- subDatDB2[,c('siteID','individualID','doy_sd','decimalLatitude','Mycorrhizal.type')] %>% unique()
    
    ggplot(subDatDB2,aes(as.numeric(as.character(doy_sd)),
                         fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year SD")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("SD in Day Of Year of Budburst in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(0,30))
    
    
    plot(density(na.omit(subDatDB2$doy_sd)),main="SD in DOY of bud burst for DB individuals",xlim=c(0,40))
    lines(density(na.omit(as.numeric(subDatDB2[subDatDB2$Mycorrhizal.type=="AM",]$doy_sd))),col="cyan")
    lines(density(na.omit(as.numeric(subDatDB2[subDatDB2$Mycorrhizal.type=="EcM",]$doy_sd))),col="red")
    legend('topright',col=c("black","cyan","red"),legend = c("All DB","AM DB","ECM DB"),lty=1,lwd=3)
    
    
```

```{r,eval=FALSE}
p <- 3 #Senescence
  print(NEON_phenophase_names[p])
  subDat <- read.csv(file=paste0(dataPath,'NEON_PhenologyObservations/NEON_PhenoObservationData_',gsub(" ","",NEON_phenophase_names[p]),'.csv'))
  subDat <- subDat %>% filter(phenophaseIntensity == mediumIntensity_phenophases[p])
  subDat$year <- as.numeric(subDat$year)
  subDat <- left_join(subDat,allPrecipData[,-3],by=c('siteID','date','year'))
  subDat <- left_join(subDat,allTempData,by=c('siteID','date','year'))
  subDat <- left_join(subDat,allSunlightTimes,by=c('siteID','date'))
  subDat <- subDat %>% filter(year!=2022)
  subDat$Mycorrhizal.type <- as.factor(subDat$Mycorrhizal.type)
  
  #Deciduous Broadleaf
  subDatDB <- subDat %>% filter(growthForm=="Deciduous broadleaf")
  subDatDB_ECM <- subDatDB %>% filter(Mycorrhizal.type=="EcM",growthForm=="Deciduous broadleaf")
  subDatDB_AM <- subDatDB %>% filter(Mycorrhizal.type=="AM",growthForm=="Deciduous broadleaf")
  
    ggplot(subDatDB,aes(as.numeric(as.character(dayOfYear)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("Day of Year")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("Day of Year of Senescence in Deciduous Broadleaf")+
  scale_x_continuous(limits=c(150,400))
    
  ggplot(subDatDB,aes(as.numeric(as.character(GDD_15)),fct_reorder(siteID,decimalLatitude),fill=Mycorrhizal.type)) +
  geom_density_ridges2(scale=1)+
  theme_classic()+
  theme(axis.text.x = element_text(angle=90))+
  xlab("GDD_15 (C)")+
  ylab("Site ID (Ordered by Latitude)")+
    ggtitle("GDD_10 of Senescence in Deciduous Broadleaf")

```


